---
title: "Week 3 Assignment"
author: "Yanyi Li"
date: "2024-09-18"
output:
  html_document: default
  pdf_document: default
---

## Overview


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tibble)
library(flextable)
```


### Normalization

```{r}
# import data
df <- read.csv('https://raw.githubusercontent.com/yli1048/yli1048/refs/heads/607/Employee%20Sample%20Data.csv', header=TRUE)
glimpse(df)
```


```{r}
#Create data frame for employee information
df1 <- df[, c(1:5, 9, 14)]
print(df1)
```



```{r}
#Create data frame for employee's salary
df2 <- df[, c(1, 10, 11)]
print(df2)
```


```{r}
#Plot histogram
hist(df2$Annual.Salary, main = "Annual Salary", xlab = "Salary")
```


```{r}
#Create data frame for workforce diversity
df3 <- df[, c(1, 6:8, 12, 13)]
print(df3)
```


```{r}
#Plot histogram
hist(df3$Age, main = "Age", xlab = "Age")
```


### Character Manipulation


##### 2. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r}
library(stringr)
```


```{r import majors}
majors <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv", header = TRUE)
glimpse(majors)
```


```{r string data}
#Subset data frame based on majors that have "DATA" or "STATISTICS"
majors[str_detect(majors$Major, "DATA|STATISTICS"),]
```


##### Majors that contains either "DATA" or "STATISTICS" are "COMPUTER PROGRAMMING AND DATA PROCESSING", "MANAGEMENT INFORMATION SYSTEMS AND STATISTICS", and "STATISTICS AND DECISION SCIENCE".



#### 3. Describe, in words, what these expressions will match:
##### (.)\1\1
The word contains the same character three times in a row. For example: AAA.

##### "(.)(.)\\2\\1"
Two consecutive characters are repeated in reverse order. For example: Alla.

##### (..)\1
Two consecutive characters are repeated. For example: Haha.

##### "(.).\\1.\\1"
The word has the same character in the first, third, and fifth positions. For example: Abaca.

##### "(.)(.)(.).*\\3\\2\\1"
The first three characters are repeated in reverse order at the end, separated by any number of characters. For example: qwerewq. 


#### 4. Construct regular expressions to match words that:

##### Start and end with the same character.
```{r 4.1}
str_subset(words, "^(.)((.*\\1$)|\\1?$)")
```


##### Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r 4.2}
str_subset("church", "([A-Za-z][A-Za-z]).*\\1")
```


##### Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r 4.3}
str_subset(words, "([a-z]).*\\1.*\\1")
```

